Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-24 2017-Xudong-SMT/OpenPNets-SMT.tex
Merge

pNets can encode naturally the notion of input actions in value-passing CCS
\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
for more general mechanisms, like gate negociation in Lotos, or broadcast
communications.
\ERIC{Formaly, value-passing actions \emph{\`a la} CCS, denoted as ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$ is a variable denoting a channel name, $?x$ is an input variable denoting the data argument received as input on $ch$, and $exp$ some data expression (containing no input variables). }
%For Lotos-style
%distributed synchronisation, we use synchronisation vectors that encode matching data
%offers on a common gate; or 
We can also use more complex action structure such as Meije-SCCS action
monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronisation constructs
will depend on the action algebra.

@@

The semantic of the open pNets is already defined as an open automaton in \cite{FORTE16} using open transitions to present the transitions of its global states.
\begin{definition}[Operational semantics of open pNets]
  \label{def:operationalSemantics}
  The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),J,\mathcal{S}, s_0,
  \mathcal{T}>$ where:
  \begin{itemize}
    \item $J$ is the indices of the holes: $Holes(p)= H_j^{j\in J}$.
    %  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
    \item $\overline{\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
    \item $\mathcal{T}$ is the smallest set of open transitions
    satisfying the rules below:
  \end{itemize}

@@

The proof can be found in \cite{FORTE16}.

>>>>

pNets can encode naturally the notion of input actions in value-passing CCS
\cite{Milner89} or of usual point-to-point message passing calculi, but it also allows
for more general mechanisms, like gate negociation in Lotos, or broadcast
communications.
\ERIC{Formally, value-passing actions \emph{\`a la} CCS, denoted as ``?ch(x)'' and ``!ch(exp)'' in our CCS running example, stand respectively for $CCSact(i(ch),?x)$ and $CCSact(ch,exp)$, where $ch$ is a variable denoting a channel name, $?x$ is an input variable denoting the data argument received as input on $ch$, and $exp$ some data expression (containing no input variables). In our example we will use the usual CCS syntax. }
%For Lotos-style
%distributed synchronisation, we use synchronisation vectors that encode matching data
%offers on a common gate; or 
We can also use more complex action structure such as Meije-SCCS action
monoids, like in $a.b$, $a^{f(n)}$ (see \cite{deSimone85}). The expressiveness of the synchronisation constructs
will depend on the action algebra.

@@

The semantic of the open pNets is already defined as an open automaton in \cite{henrio:Forte2016} using open transitions to present the transitions of its global states.
\begin{definition}[Operational semantics of open pNets]
  \label{def:operationalSemantics}
  The semantics of a pNet $p$ is an open automaton $A = <Leaves(p),J,\mathcal{S}, s_0,
  \mathcal{T}>$ where:
  \begin{itemize}
    \item $J$ is the indices of the holes: $Holes(p)= H_j^{j\in J}$.
    %  \item $\overline{L}^L = Leaves(p), \overline{H}^J = Holes(p)$
    \item $\overline{\mathcal{S}} = States(p)$ and $s_0 = InitState(p)$
    \item $\mathcal{T}$ is the smallest set of open transitions
    satisfying the rules below:
  \end{itemize}

@@

The proof can be found in \cite{henrio:Forte2016}.
